Gaussian Process regression for astronomical time-series

### 2022-08-20 src/tex/ms.tex
[showyourwork] overleaf sync

Some popular kernels are listed in \autoref{tab:kernels}, and some other choices are discussed in Chapter 4 of \citet{gpml}.
In any practical application, these kernel functions are not used on their own.
Instead, more expressive models are designed by combining these models.
In particular, any valid kernel functions can be added or multiplied to generate new valid functions.
For example, the squared exponential kernel function is generally defined as
\begin{equation}
  k(\dt;\,\hyperparams) = \amplitude^2\,\exp\left(-\frac{\dt^2}{2\,\lengthscale^2}\right)
\end{equation}
with $\hyperparams = \{\amplitude,\,\lengthscale\}$, which, in our notation, is actually the product of a constant kernel and a squared exponential kernel, as defined in \autoref{tab:kernels}.
Another example that is commonly used in the astrophysics literature is the following ``quasi-periodic'' kernel
\begin{equation}
  k(\dt;\,\hyperparams) = \amplitude^2\,\exp\left(-\frac{\dt^2}{2\,{\lengthscale_1}^2} -\gamma\,\sin^2\left[\frac{\pi\,\dt}{\lengthscale_2}\right] \right)
\end{equation}
with $\hyperparams = \{\amplitude,\,\lengthscale_1,\,\lengthscale_2,\,\gamma\}$, which has a period of $\lengthscale_2$, and a decoherence timescale of $\lengthscale_1$.

@@

>>>>

\subsubsection{Standard kernels \& sums or products thereof}

Some popular kernels are listed in \autoref{tab:kernels}, and some other choices are discussed in Chapter 4 of \citet{gpml}.
In any practical application, these kernel functions are not used on their own.
Instead, more expressive models are designed by combining these models.
In particular, any valid kernel functions can be added or multiplied to generate new valid functions.
For example, the squared exponential kernel function is generally defined as
\begin{equation}
  k(\dt;\,\hyperparams) = \amplitude^2\,\exp\left(-\frac{\dt^2}{2\,\lengthscale^2}\right)
\end{equation}
with $\hyperparams = \{\amplitude,\,\lengthscale\}$, which, in our notation, is actually the product of a constant kernel and a squared exponential kernel, as defined in \autoref{tab:kernels}.
Another example that is commonly used in the astrophysics literature \dan{ADD SOME CITATIONS} is the following ``quasi-periodic'' kernel
\begin{equation}
  k(\dt;\,\hyperparams) = \amplitude^2\,\exp\left(-\frac{\dt^2}{2\,{\lengthscale_1}^2} -\gamma\,\sin^2\left[\frac{\pi\,\dt}{\lengthscale_2}\right] \right)
\end{equation}
with $\hyperparams = \{\amplitude,\,\lengthscale_1,\,\lengthscale_2,\,\gamma\}$, which has a period of $\lengthscale_2$, and a decoherence timescale of $\lengthscale_1$.

@@

\subsubsection{Operations on kernel functions}

Derivatives, integrals, etc.

\begin{figure}[ht]
  \centering
  \script{kernel-ops.ipynb}
  \includegraphics[width=\linewidth]{figures/kernel-ops1.pdf}
  \includegraphics[width=\linewidth]{figures/kernel-ops2.pdf}
  \includegraphics[width=\linewidth]{figures/kernel-ops3.pdf}
  \caption{Derivative kernels.}
  \label{fig:kernel-ops}
\end{figure}

\subsubsection{Multi-dimensional inputs}

Abs vs other norms, non-standard geometry (GPs on the sphere), parallel time series.

\subsubsection{Physically motivated kernels}

Cosmology, asteroseismology, etc.
